Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-13 paper/main.tex
small additions

We also performed a simple study to find evidence of halo properties,
other than mass, in driving the alignments. We find that in the case of
shape, halos located in high density regions or with a low value of
the reduced spin parameter tend to show a stronger signal. This is
more pronounced in the Tweb than in the Vweb. Concerning angular
momentum we find that the antialignment signal is stronger for halos
with high spin values. In the peculiar velocities we do not find any
affect in the Tweb alignments.

>>>>

We also performed a simple study to find evidence of halo properties,
other than mass, in driving the alignments. We find that in the case of
shape, halos located in high density regions or with a low value of
the reduced spin parameter tend to show a stronger signal. This trend is
more pronounced in the Tweb than in the Vweb. Concerning angular
momentum we find that the antialignment signal is stronger for halos
with high spin values. In the peculiar velocities we do not find any
effect in the Tweb alignments, and the results for the Vweb show a
wide variations with grid resolution that impedes driving any strong
conclusion.
